---
title: "Lab 00 - Hello IDS!"
author: "Lim Zhen Yang"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Lim Zhen Yang", "Yuchun Zhu", "Mingshi Yue", 
           "Kevin Jiang", "Guo Yifan"),
  github_username = c("yangsubwayceo", "messi15", "EthanYue123", 
                      "jky040223", "Alen0504"), 
  colour = c("gray", "blue", "yellow", 
             "yellow", "green"),
  hobby = c("listening to music", "football", "woman", 
            "basketball", "playing chess"),
  favourite_number = c(7, 10, 6, 4, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows each team members' favourite number.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "username", 
          y = "number",
          title = "Favourite Number of Team Members")
```

labs() is a function to change plot labels for new labels. It allows the user to add titles as well.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The bar plot is not a good data visualisation because it requires multiple members to have the same hobby. 
In a diverse array of students, the probability of students sharing the same hobby increases, 
however number of students with unique hobbies increases as well, leading to a bar plot with a lot of "1-height bars". 
An efficient way of visualising information would be to group students' hobbies under similar hobby groups such as 'sports',
'entertainment', 'arts', 'culinary' etc. and then make a bar plot of the frequency of students' hobby groups.
